NFC and burnout in teachers - A replication and extension study

### 2022-02-11 Manuscript/Manuscript.Rmd
knits properly

---
title             : "NFC and burnout in teachers - A replication and extension study"
shorttitle        : "NFC and burnout in teachers"

author: 
  - name          : "Josephine Zerna"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Nicole Engelmann"
    affiliation   : "2"
    role:
      - Conceptualization
      - Investigation
      - Writing - review & editing
  - name          : "Anja Strobel"
    affiliation   : "3"
    role:
      - Conceptualization
      - Supervision
      - Methodology
      - Writing - review & editing
  - name          : "Alexander Strobel"
    affiliation   : "1"
    role:
      - Conceptualization
      - Supervision
      - Methodology
      - Writing - review & editing

@@

abstract: |
  The prevalence of burnout has been rising for years, not just due to the increasing demands during the Covid-19 pandemic.
  While it is known that burnout primarily affects employees in social jobs, less is known about the personality traits that promote or protect against burnout.
  One of these traits is Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.
  In the present study, we analyzed questionnaire data of teachers that had been collected in spring of 2020.
  Firstly, we aimed to replicate results by Grass et al. (2018), who showed that the association of NFC and the burnout aspect of reduced personal efficacy was mediated by habitual use of reappraisal, but not by habitual suppression or self-control.
  With our data, self-control became a significant mediator when teaching experience was being taken into account, but neither reappraisal nor suppression mediated between NFC and reduced personal efficacy.
  Secondly, we computed a structural equation model to investigate whether NFC and burnout were associated via different ratios of demands and personal resources.
  The hypothesized model did not have good fit, but indicated that individuals high in NFC have lower burnout scores due to demands that either fit their resources or do not exceed them.

keywords          : "mediation, resources, demands, structural equation modelling, Covid-19"
wordcount         : "X"

bibliography      : NFC_Burnout.bib

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf

csl               : apa.csl # this is a workaround for a current bug in the papaja/Rmd software, which fails to shorten multiple authors to "et al."

header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
---

```{r setup, include = FALSE}
library(papaja)
library(bibtex)

#install.packages("here")       # easy file referencing
#install.packages("tidyverse")  # plotting and managing data
#install.packages("lavaan")     # for structural equation modelling
#install.packages("psych")      # Cronbach's Alpha and such
#install.packages("MVN")        # Mardia's test and such
#install.packages("MBESS")      # MacDonald's Omega
#install.packages("Hmisc")      # for correlations with p-values
#install.packages("kableExtra") # for great tables (see haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf)
#install.packages("knitr")      # for knitting documents and tables
#install.packages("semPlot")    # plotting path models
#install.packages("remotes")    # for APA output (remotes::install_github("dgromer/apa"))
#install.packages("ppcor")      # for partial correlations

library(here)
library(tidyverse)
library(ggplot2)
library(lavaan)
library(psych)
library(MVN)
library(MBESS)
library(Hmisc)
library(kableExtra)
library(knitr)
library(GGally)                 # from ggplot2, for multi-correlation plots
library(semPlot)
library(qgraph)
library(apa)                    # from the remotes package
library(ppcor)

@@

```{r analysis-preferences, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r correlations_table, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r objective1_table, echo=FALSE, message=FALSE, warning=FALSE}

@@

  Table3 <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
                                   "NFC $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
                                   "Total Effect"),
                          "$B$" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit_summ$PE$ci.lower[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fit_summ$PE$std.all[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

```{r objective1_plot, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}

@@

```{r objective1years_table, echo=FALSE, message=FALSE, warning=FALSE}

@@

  Table4 <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "Years spent teaching $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
                                   "NFC and years spent teaching $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
                                   "Total Effect"),
                          "$B$" = c(fityears_summ$PE$est[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fityears_summ$PE$se[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fityears_summ$PE$z[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fityears_summ$PE$pvalue[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fityears_summ$PE$ci.lower[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fityears_summ$PE$ci.upper[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fityears_summ$PE$std.all[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

```{r objective1years_plot, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}

@@

```{r objective2_plot, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}

@@

```{r objective2_table, echo=FALSE, message=FALSE, warning=FALSE}

@@

  Table5 <- data.frame("Path" = c("NFC $\\rightarrow$ DTH", "NFC $\\rightarrow$ DTL", "NFC $\\rightarrow$ DRF", "NFC $\\rightarrow$ MBI",
                                      "DTH $\\rightarrow$ MBI", "DTL $\\rightarrow$ MBI", "DRF $\\rightarrow$ MBI",
                                      "NFC $\\rightarrow$ MBI via DTH", "NFC $\\rightarrow$ MBI via DTL", "NFC $\\rightarrow$ MBI via DRF",
                                      "Total Effect"),
                          "$B$" = c(fit2_summ$PE$est[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fit2_summ$PE$se[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fit2_summ$PE$z[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fit2_summ$PE$pvalue[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit2_summ$PE$ci.lower[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit2_summ$PE$ci.upper[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fit2_summ$PE$std.all[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

```{r exploring_badfit, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r exploratory1_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}

@@

```{r exploratory1_table, echo=FALSE, message=FALSE, warning=FALSE}

@@

  TableS1 <- data.frame("Path" = c("NFC $\\rightarrow$ DTH", "NFC $\\rightarrow$ DTL", "NFC $\\rightarrow$ DRF", "NFC $\\rightarrow$ RPE",
                                      "DTH $\\rightarrow$ RPE", "DTL $\\rightarrow$ RPE", "DRF $\\rightarrow$ RPE",
                                      "NFC $\\rightarrow$ RPE via DTH", "NFC $\\rightarrow$ RPE via DTL", "NFC $\\rightarrow$ RPE via DRF",
                                      "Total Effect"),
                          "$B$" = c(fit_explor1_summ$PE$est[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fit_explor1_summ$PE$se[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fit_explor1_summ$PE$z[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit_explor1_summ$PE$ci.lower[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit_explor1_summ$PE$ci.upper[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

  explor2_model <- '
  measurement model
    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
    DTH =~ dth1 + dth2 + dth3
    DRF =~ drf1 + drf2 + drf3

@@

```{r explor2_plot, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r explor2_table, echo=FALSE, message=FALSE, warning=FALSE}

@@

  TableS2 <- data.frame("Path" = c("Years $\\rightarrow$ COVB", "Years $\\rightarrow$ SCS",
                                   "COVB $\\rightarrow$ DTH", "SCS $\\rightarrow$ DTH", "NFC $\\rightarrow$ DTH",
                                   "SCS $\\rightarrow$ DRF", "NFC $\\rightarrow$ DRF",
                                   "DTH $\\rightarrow$ EE", "COVB $\\rightarrow$ EE", "DRF $\\rightarrow$ RPE",
                                   "NFC and Years $\\rightarrow$ RPE via SCS and DRF",
                                   "NFC and Years $\\rightarrow$ EE via SCS, COVB, and DTH",
                                   "Total Effect"),
                          "$B$" = c(fit_explor2_summ$PE$est[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fit_explor2_summ$PE$se[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fit_explor2_summ$PE$z[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit_explor2_summ$PE$ci.lower[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit_explor2_summ$PE$ci.upper[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

>>>>

---
title             : "NFC and burnout in teachers - A replication and extension study"
shorttitle        : "NFC and burnout in teachers"
author: 
  - name          : "Josephine Zerna"
    affiliation   : "1"
    orcid         : "0000-0003-2892-884X"
    corresponding : yes    # Define only one corresponding author
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Nicole Engelmann"
    affiliation   : "2"
    role:
      - Conceptualization
      - Investigation
      - Writing - review & editing
  - name          : "Anja Strobel"
    affiliation   : "3"
    orcid         : "0000-0002-0313-0615"
    role:
      - Conceptualization
      - Supervision
      - Methodology
      - Writing - review & editing
  - name          : "Alexander Strobel"
    affiliation   : "1"
    orcid         : "0000-0002-9426-5397"
    role:
      - Conceptualization
      - Supervision
      - Methodology
      - Writing - review & editing

@@

abstract: |
  The prevalence of burnout has been rising for years, not just due to the increasing demands during the Covid-19 pandemic.
  While it is known that burnout primarily affects employees in social jobs, less is known about the personality traits that promote or protect against burnout.
  One of these traits is Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.
  In the present study, we analyzed questionnaire data of N\ =\ 180 teachers that had been collected in spring of 2020.
  Firstly, we aimed to replicate results by Grass et al. (2018), who showed that the association of NFC and the burnout aspect of reduced personal efficacy was mediated by habitual use of reappraisal, but not by habitual suppression or self-control.
  With our data, self-control became a significant mediator when teaching experience was being taken into account, but neither reappraisal nor suppression mediated between NFC and reduced personal efficacy.
  Secondly, we computed a structural equation model to investigate whether NFC and burnout were associated via different ratios of demands and personal resources, and included other variables in an exploratory approach.
  The results indicated that teachers with higher NFC and more self-control have lower burnout because they experience their resources as fitting to the demands.

keywords          : "mediation, resources, demands, structural equation modelling, Covid-19"
wordcount         : "X"
bibliography      : NFC_Burnout.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : apa.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage{chngcntr}
---
\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\setcounter{figure}{0}

```{r setup, include = FALSE}

  # set the output for figures and tables to the width of the text throughout the entire script

  knitr::opts_chunk$set(out.width = "\\textwidth")

  # define required packages

  packages = c("bibtex", "here", "tidyverse", "bayestestR", "papaja", "lavaan", "psych", "MVN", "MBESS",
               "kableExtra", "Hmisc", "semPlot", "ggplot2", "knitr", "qgraph", "ppcor")

  # check whether each package is installed and install and/or load library

  installed_packages <- packages %in% rownames(installed.packages())
  if (any(installed_packages == FALSE)) {
    install.packages(packages[!installed_packages])
  }
  invisible(lapply(packages, library, character.only = TRUE))

  # those two libraries come from packages with different names, so we load them individually

  library(GGally)                 # from ggplot2, for multi-correlation plots
  library(apa)                    # from the remotes package

@@

```{r analysispreferences, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r correlationstable, echo=FALSE, message=FALSE, warning=FALSE, caption="Correlations and internal consistencies"}

@@

```{r objective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018)"}

@@

  Table3 <- data.frame("Path" = c("NFC on Self Control", "NFC on Reappraisal", "NFC on Suppression",
                                   "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
                                   "NFC on RPE via Self Control", "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
                                   "Total Effect"),
                          "$B$" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit_summ$PE$ci.lower[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fit_summ$PE$std.all[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

```{r objective1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Replication of Grass et al. (2018)"}

@@

```{r objective1yearstable, echo=FALSE, message=FALSE, warning=FALSE}

@@

  Table4 <- data.frame("Path" = c("NFC on Self Control", "Years spent teaching on Self Control",
                                  "NFC on Reappraisal", "NFC on Suppression",
                                  "Self Control on RPE", "Reappraisal on RPE", "Suppression on RPE", "NFC on RPE",
                                  "NFC and years spent teaching on RPE via Self Control",
                                  "NFC on RPE via Reappraisal", "NFC on RPE via Suppression",
                                  "Total Effect"),
                          "$B$" = c(fityears_summ$PE$est[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fityears_summ$PE$se[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fityears_summ$PE$z[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fityears_summ$PE$pvalue[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fityears_summ$PE$ci.lower[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fityears_summ$PE$ci.upper[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fityears_summ$PE$std.all[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

```{r objective1yearsplot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}

@@

```{r objective2plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Mediation of NFC and burnout by demand-resource-ratios"}

@@

```{r objective2table, echo=FALSE, message=FALSE, warning=FALSE}

@@

  Table5 <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on MBI",
                                      "DTH on MBI", "DTL on MBI", "DRF on MBI",
                                      "NFC on MBI via DTH", "NFC on MBI via DTL", "NFC on MBI via DRF",
                                      "Total Effect"),
                          "$B$" = c(fit2_summ$PE$est[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fit2_summ$PE$se[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fit2_summ$PE$z[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fit2_summ$PE$pvalue[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit2_summ$PE$ci.lower[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit2_summ$PE$ci.upper[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fit2_summ$PE$std.all[fit2_summ$PE$label != "" & fit2_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

```{r exploringbadfit, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r exploratory1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}

@@

```{r exploratory1table, echo=FALSE, message=FALSE, warning=FALSE}

@@

  TableS1 <- data.frame("Path" = c("NFC on DTH", "NFC on DTL", "NFC on DRF", "NFC on RPE",
                                      "DTH on RPE", "DTL on RPE", "DRF on RPE",
                                      "NFC on RPE via DTH", "NFC on RPE via DTL", "NFC on RPE via DRF",
                                      "Total Effect"),
                          "$B$" = c(fit_explor1_summ$PE$est[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fit_explor1_summ$PE$se[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fit_explor1_summ$PE$z[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fit_explor1_summ$PE$pvalue[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit_explor1_summ$PE$ci.lower[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit_explor1_summ$PE$ci.upper[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fit_explor1_summ$PE$std.all[fit_explor1_summ$PE$label != "" & fit_explor1_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

  explor2_model <- '
  # measurement model
    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
    DTH =~ dth1 + dth2 + dth3
    DRF =~ drf1 + drf2 + drf3

@@

```{r explor2plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Exploratory analysis of variable relations"}

@@

```{r explor2table, echo=FALSE, message=FALSE, warning=FALSE}

@@

  TableS2 <- data.frame("Path" = c("Years on COVB", "Years on SCS",
                                   "COVB on DTH", "SCS on DTH", "NFC on DTH",
                                   "SCS on DRF", "NFC on DRF",
                                   "DTH on EE", "COVB on EE", "DRF on RPE",
                                   "NFC and Years on RPE via SCS and DRF",
                                   "NFC and Years on EE via SCS, COVB, and DTH",
                                   "Total Effect"),
                          "$B$" = c(fit_explor2_summ$PE$est[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fit_explor2_summ$PE$se[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fit_explor2_summ$PE$z[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fit_explor2_summ$PE$pvalue[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit_explor2_summ$PE$ci.lower[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit_explor2_summ$PE$ci.upper[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fit_explor2_summ$PE$std.all[fit_explor2_summ$PE$label != "" & fit_explor2_summ$PE$label != "Contrast"]),
                          check.names = FALSE)
